Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - return sd

  sd_team <- purr::map(
    brm_model$model,
    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
      dplyr::pull()
  ) %>%
  unlist()

@@

```{r run-sims}
sample_sims <- tibble(
  n_teams = n_ts_qs$n_teams,
  quants = n_ts_qs$quantiles,
  models = map2(
    n_teams, quants,
    ~run_simulations(.x, .y)
  )
)

>>>>

  sd_team <- as_tibble(summary(brm_model)$team)

@@

```{r run-sims}
sample_sims <- tibble(
  n_teams = n_ts_qs$n_teams,
  quants = n_ts_qs$quantiles,
  sd_team = map2(
    n_teams, quants,
    ~run_simulations(.x, .y)
  )
)
